Critical assessment of Linear-Response Excitations in Molecular system\\ or \\ On the Localization of the Linear-Response excitations in Open Systems

### 2018-01-05 LRDraft.tex
update

We introduce the \emph{excitonic states} defined via the linear combination of the basis set orthogonal to $\dmnot$ with the
coefficients that appears in \eqref{XYcoeffDef1}, that is:
\begin{align}
\ket{\phi^E_p} &\equiv \sint \dd \alpha X_{E}^{p \alpha} \ket{\psi(\alpha)} &
\tbra{\phi^E_p} &\equiv \sint \dd \alpha {\tilde X_{E}^{p \alpha}} \bra{\psi(\alpha)} \;, \nn\\
\bra{\chi^E_p} &\equiv \sint \dd \alpha  Y_{E}^{p \alpha} \bra{\psi(\alpha)} &
\tket{\chi^E_p} &\equiv \sint \dd \alpha {\tilde Y}_{E}^{p\alpha} \ket{\psi(\alpha)} \;.
\end{align}
Thanks to these definitions we can express the excitation operators as follows:
\be\lb{ExctitationOperatorsDef2}
\op E = \sum_p \left( \ket{\phi^E_p}\bra{\psi_p} + \ket{\psi_p} \bra{\chi^E_p}\right)\;, \qq
\op {\tilde E} = \sum_p \left( \ket{\psi_p} \tbra{\phi^E_p} + \tket{\chi^E_p}\bra{\psi_p} \right)\;.
\ee
The operator eigenvalue equations \eqref{opEeigenvalueDef1} and \eqref{optildeEeigenvalueDef1} can be translated in Schroedinger-like equations
for the excitonic states.

>>>>

We introduce the \emph{excitonic states} defined via the linear combination of the basis set orthogonal to $\dmnot$ with the
coefficients that appears in \eqref{XYcoeffDef1}, that is:
\begin{align}
\ket{\phi^E_p} &\equiv \sint \dd \alpha X_{E}^{p \alpha} \ket{\psi(\alpha)} &
\tbra{\phi^E_p} &\equiv \sint \dd \alpha {\tilde X_{E}^{p \alpha}} \bra{\psi(\alpha)} \;, \nn\\
\bra{\chi^E_p} &\equiv \sint \dd \alpha  Y_{E}^{p \alpha} \bra{\psi(\alpha)} &
\tket{\chi^E_p} &\equiv \sint \dd \alpha {\tilde Y}_{E}^{p\alpha} \ket{\psi(\alpha)} \;.
\end{align}
Thanks to these definitions we can express the excitation operators as follows:
\be\lb{ExctitationOperatorsDef2}
\op E = \sum_p \left( \ket{\phi^E_p}\bra{\psi_p} + \ket{\psi_p} \bra{\chi^E_p}\right)\;, \qq
\op {\tilde E} = \sum_p \left( \ket{\psi_p} \tbra{\phi^E_p} + \tket{\chi^E_p}\bra{\psi_p} \right)\;.
\ee
The operator eigenvalue equations \eqref{opEeigenvalueDef1} and \eqref{optildeEeigenvalueDef1} can be translated into a Schroedinger-like equations
for the excitonic states.
